Brownian Dynein Model

### 2015-09-18 latex/derivation.tex
Adding changes to the bothbound solution.

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &= L_{s}*\cos(\Theta_{nb}) \\
  X_{t}  &= ?? \\
  X_{fm} &= L_{s}*\cos(\Theta_{fb}) \\
  X_{fb} &= L \\
\end{align}

@@

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{nb} &= 0 \\
  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{nm} - X_{nb}) + \lambda_{bt}(X_{t } - X_{nm}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{nm}) + \lambda_{bt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{nb} &= 0 \\
  \dot{Y}_{nm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{nm} - Y_{nb}) + \lambda_{bt}(Y_{t } - Y_{nm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{nm}) + \lambda_{bt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
\end{align}

>>>>

Also by the law of cosines, we can see that:

\begin{equation}
   \Theta_{1} = \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})
\end{equation}

We use this to find the value of $X_{t}$ and $Y_{t}$:

\begin{align}
  X_{t} &= L_n\cos(\Theta_{1}) \\
       &= \frac{L^2+L_n^2-L_f^2}{2L} \\
       &= \frac{L^2 + L_s^2 + L_t^2 - 2L_tL_s\cos(\Theta_{nm}) - L_s^2 - L_t^2 + 2L_sL_t\cos(\Theta_{fm})}{2L} \\
       &= \frac{L^2 + 2L_tL_s\big(\cos(\Theta_{fm})-\cos(\Theta_{nm})\big)}{2L}
\end{align}

and

\begin{align}
  Y_{t} &= L_n\sin(\Theta_{1}) \\
        &=
\end{align}

This is getting ugly and complicated. I will not do it. I will do it when I need to. \\
\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &= L_{s}*\cos(\Theta_{nb}) \\
  X_{t}  &= ?? \\
  X_{fm} &= L_{s}*\cos(\Theta_{fb}) \\
  X_{fb} &= L \\
\end{align}

@@

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{nb} &= \frac{1}{\gamma} \Big(F_{xnb} + \lambda_{fs}(X_{nm} - X_{nb})\Big) + R_{xnb} \\
  \dot{X}_{nm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{bs}(X_{nm} - X_{nb}) + \lambda_{bt}(X_{t } - X_{nm}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{bt}(X_{t } - X_{nm}) + \lambda_{bt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{bt}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{fs}(X_{fb} - X_{fm})\Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{nb} &= \frac{1}{\gamma} \Big(F_{ynb} + \lambda_{fs}(Y_{nm} - Y_{nb})\Big) + R_{ynb} \\
  \dot{Y}_{nm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{bs}(Y_{nm} - Y_{nb}) + \lambda_{bt}(Y_{t } - Y_{nm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{bt}(Y_{t } - Y_{nm}) + \lambda_{bt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{bt}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{fs}(Y_{fb} - Y_{fm})\Big) + R_{ybr}
\end{align}
